Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-15 WSSSPE2_report/WSSSPE2_review.tex
Remove duplicate
Add reference to WSSSPE2 collaborative notes

\todo{VOLUNTEER NEEDED to neaten this - add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

@@

Mike Rilee                    \\

>>>>

The following is a partial list of workshop attendees who registered on the
collaborative notes document~\cite{WSSSPE2-google-notes} that was being used
for live note taking at the workshop, with some additions from
attendees to breakout groups.

@@
